Coupled response of stomatal and mesophyll conductance to light enhances photosynthesis of shade leaves under sunflecks.

### 2016-06-19 gm_newphyt/manuscript_gmes.Rmd
use pacman for package loading

```{r install packages, echo=FALSE, message=FALSE, warning=FALSE,results="hide"}
#install needed packages if not already installed
.packages = c("lubridate", "doBy", "plyr","plotrix", "wesanderson", "plantecophys", "scales","reshape", "pixiedust")

# Install CRAN packages (if not already installed)
.inst <- .packages %in% installed.packages()
if(length(.packages[!.inst]) > 0) install.packages(.packages[!.inst], repos = "http://cran.at.r-project.org")

# Load packages into session
lapply(.packages, library, character.only=TRUE)
```

>>>>

```{r install packages, echo=FALSE, message=FALSE, warning=FALSE,results="hide"}
r <- require(pacman)
if(!r)install.packages("pacman")
pacman::p_load(lubridate, doBy, plyr,plotrix, wesanderson, plantecophys, scales,reshape, pixiedust)
```
